Kernel k-Groups via Hartigan's Method

### 2018-08-13 energy_clustering/pami18/energy_clustering.tex
pami

\author{Guilherme~Fran\c ca,~Maria Rizzo~and~Joshua T.~Vogelstein
\IEEEcompsocitemizethanks{
\IEEEcompsocthanksitem G. Fran\c ca
is with the Mathematical Institute for Data Science (MINDS), Johns Hopkins
University.\protect \\
E-mail: guifranca@jhu.edu
\IEEEcompsocthanksitem J. Vogelstein is 
with the Center for Imaging Science, 
the Department of Biomedical Engineering and Institute for Computational
Medicine, Johns Hopkins University. \protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: jovo@jhu.edu
\IEEEcompsocthanksitem M. Rizzo is with the Department of Mathematics
and Statistics, Bowling Green State University. \protect\\
E-mail: mrizzo@bgsu.edu}% <-this % stops an unwanted space
\thanks{Manuscript received August 14, 2018; revised August 14, 2018.}}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio,height=1.30in]{rizzo.jpg}}]{Maria Rizzo}
holds a BS and MA degree in Mathematics from the University of Toledo, a MS in
Applied Statistics from BGSU, and a PhD from BGSU in 2002. After four years as
Assistant Professor at Ohio University Department of Mathematics, she 
returned to BGSU in 2006, where she is currently Professor of Statistics 
in the Department of
Mathematics and Statistics. Her primary research interests are 
centered on energy
statistics, distance correlation and its applications, computational
statistics, and related topics. In addition to teaching statistics, data
science, and actuarial science, she enjoys writing textbooks about statistical
computing and using R software. She has a forthcoming research 
monograph on energy
statistics (joint with G. Szekely) and also other book writing projects under
contract as well.
\end{IEEEbiography}

>>>>

\author{Guilherme~Fran\c ca,~Maria L.~Rizzo~and~Joshua T.~Vogelstein
\IEEEcompsocitemizethanks{
\IEEEcompsocthanksitem G. Fran\c ca
is with the Mathematical Institute for Data Science (MINDS), Johns Hopkins
University.\protect \\
E-mail: guifranca@jhu.edu
\IEEEcompsocthanksitem J. T. Vogelstein is 
with the Center for Imaging Science, 
the Department of Biomedical Engineering and Institute for Computational
Medicine, Johns Hopkins University. \protect\\
% note need leading \protect in front of \\ to get a newline within \thanks as
% \\ is fragile and will error, could use \hfil\break instead.
E-mail: jovo@jhu.edu
\IEEEcompsocthanksitem M. L. Rizzo is with the Department of Mathematics
and Statistics, Bowling Green State University. \protect\\
E-mail: mrizzo@bgsu.edu}% <-this % stops an unwanted space
\thanks{Manuscript received August 14, 2018; revised August 14, 2018.}}

@@

\begin{IEEEbiography}[{\includegraphics[width=1in,clip,keepaspectratio,height=1.30in]{rizzo.jpg}}]{Maria~L.~Rizzo}
holds a BS and MA degree in Mathematics from the University of Toledo, a MS in
Applied Statistics from BGSU, and a PhD from BGSU in 2002. After four years as
Assistant Professor at Ohio University Department of Mathematics, she 
returned to BGSU in 2006, where she is currently Professor of Statistics 
in the Department of
Mathematics and Statistics. Her primary research interests are 
centered on energy
statistics, distance correlation and its applications, computational
statistics, and related topics. In addition to teaching statistics, data
science, and actuarial science, she enjoys writing textbooks about statistical
computing and using R software. She has a forthcoming research 
monograph on energy
statistics (joint with G. Szekely) and also other book writing projects under
contract as well.
\end{IEEEbiography}
